\mytitile\\~

### 2020-01-22 document.tex
Probabilities

The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}. Using the corrected eigenstates $\ket{k}$ and neglecting small terms, we obtain the following expressions for the transition rates per unit time\cite{faisal2013theory}:
\begin{equation}
\begin{aligned}
R^{(2)}_{1\rightarrow 6} &\approx 2\pi\Omega_2^4 
\frac{18 J^4 \left(2 \alpha + 
\text{$\Omega_1$}\right)^2}{\alpha 
^{6}\Omega_1^2},\\
R^{(2)}_{2\rightarrow 5} &\approx 2\pi\Omega_2^4 
\frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
		$}\right)^2}{\alpha ^{6}\Omega_1^2},
\end{aligned}\label{eq:rates}
\end{equation}
when $\alpha \gg \Omega_1, \Omega_2, J$ which is 
true for our setup. From \autoref{eq:rates} 
follows that the sideband transitions are 
prohibited without the interaction in the SAM 
$(J=0)$, and the extra avoided crossings will not 
be observed.

@@

Let's consider a time-dependent perturbation $\hat V(t) = \hat V \cos{\omega_d t}$ to the unperturbed Hamiltonian $\hat H$. In the interaction picture, the Schrödinger equation looks as 

@@

	\bra{f}U^{(1)}(t,-\infty)\ket{i}&=-\frac{i}{\hbar}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\\ &=-\frac{i}{2\hbar}\big[\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}-\omega_d)\tau_1}\bra{f}\hat{V}\ket{i}+\\
	&\quad\quad\quad\quad\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}+\omega_d)\tau_1}\bra{f}\hat{V}\ket{i}\big].

@@

	\bra{f}U^{(2)}(t, -\infty)\ket{i}=\\\frac{2\pi i}{4\hbar^2}\bigg[\delta(\omega_{if}+2\omega_d)\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}+\omega_d}+\\
	\delta(\omega_{if})\bigg(\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}+\omega_d}+\\
	\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg)+\\
	\delta(\omega_{if}-2\omega_d)\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg].

@@

In overall, for $\omega_d=\omega_{if}/2$:

@@

	W^{(2)}_{i\rightarrow f}&=\frac{\pi}{8\hbar^4}\bigg|\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg|^2\delta(\omega_{if}-2\omega_d)\\ 
	&=R_{i\rightarrow f}^{(2)}\delta(\omega_{if}-2\omega_d).

@@

For our case, $\hat V = \hbar \Omega_2 (\hat b + \hat b^\dag),\ \omega_d = \delta$ which leads to \eqref{eq:rates}.

>>>>

The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}. Using the corrected eigenstates $\ket{k}$ and neglecting small terms, we obtain the following expressions for the transition rates per unit time\cite{faisal2013theory}:
\begin{equation}
\begin{aligned}
R^{(2)}_{1\rightarrow 6} &\approx \pi\Omega_2^4 
\frac{16 J^4 \left(3 \alpha^2 + 
\text{$7\Omega_1^2$}\right)^2}{\alpha 
^{10}},\\
R^{(2)}_{5\rightarrow 2} &\approx \pi\Omega_2^4 
\frac{4 J^4 \left(5 \alpha - \text{$3\Omega_1
		$}\right)^2}{\alpha ^{8}},
\end{aligned}\label{eq:rates}
\end{equation}
when $\alpha \gg \Omega_1, \Omega_2, J$ which is 
true for our setup. From \autoref{eq:rates} 
follows that the sideband transitions are 
prohibited without the interaction in the SAM 
$(J=0)$, and the extra avoided crossings will not 
be observed.

@@

Let's consider a time-dependent perturbation $\hat V(t) =\frac{\hbar\Omega_{2}}{2}(\hat{c}e^{i\omega_d t}+\hat{c}^{\dagger}e^{-i\omega_d t}) $ to the unperturbed Hamiltonian $\hat H$. In the interaction picture, the Schrödinger equation looks as 

@@

	\bra{f}U^{(1)}(t,-\infty)\ket{i}&=-\frac{i}{\hbar}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\\ &=-\frac{i\Omega_2}{2}\big[\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}-\omega_d)\tau_1}\bra{f}\hat{c}^{\dagger}\ket{i}+\\
	&\quad\quad\quad\quad\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}+\omega_d)\tau_1}\bra{f}\hat{c}\ket{i}\big].

@@

	\bra{f}U^{(2)}(t, -\infty)\ket{i}=\\\frac{2\pi i\Omega_2^2}{4}\bigg[\delta(\omega_{if}+2\omega_d)\sum_j\frac{\bra{f}\hat{c}\ket{j}\bra{j}\hat{c}\ket{i}}{\omega_{ij}+\omega_d}+\\
	\delta(\omega_{if})\bigg(\sum_j\frac{\bra{f}\hat{c}^{\dagger}\ket{j}\bra{j}\hat{c}\ket{i}}{\omega_{ij}+\omega_d}+\\
	\sum_j\frac{\bra{f}\hat{c}\ket{j}\bra{j}\hat{c}^{\dagger}\ket{i}}{\omega_{ij}-\omega_d}\bigg)+\\
	\delta(\omega_{if}-2\omega_d)\sum_j\frac{\bra{f}\hat{c}^{\dagger}\ket{j}\bra{j}\hat{c}^{\dagger}\ket{i}}{\omega_{ij}-\omega_d}\bigg].

@@

A two-photon emission:

@@

	W^{(2)}_{i\rightarrow f}&=\frac{\pi\Omega_2^4}{8}\bigg|\sum_j\frac{\bra{f}\hat{c}\ket{j}\bra{j}\hat{c}\ket{i}}{\omega_{ij}+\omega_d}\bigg|^2\delta(\omega_{if}+2\omega_d)\\ 
	&=R_{i\rightarrow f}^{(2)}\delta(\omega_{if}+2\omega_d).

@@

A two-photon absorption:
\begin{equation}\label{prob1}
\begin{aligned}
W^{(2)}_{f\rightarrow i}&=\frac{\pi\Omega_2^4}{8}\bigg|\sum_j\frac{\bra{f}\hat{c}^{\dagger}\ket{j}\bra{j}\hat{c}^{\dagger}\ket{i}}{\omega_{ij}-\omega_d}\bigg|^2\delta(\omega_{if}-2\omega_d)\\ 
&=R_{f\rightarrow i}^{(2)}\delta(\omega_{if}-2\omega_d).
\end{aligned}
\end{equation}

For our case, $ \omega_d = \delta$ which leads to \eqref{eq:rates}.
